---
title: 'Analysis: Judicial public relations: Determinants of press release publication by constitutional courts'
author: "Philipp Meyer"
date: "20 12 2019"
output:
  html_document: default
  pdf_document: default
---

Run source outside of chunk if it does not work. The same goes for everything that saves or loads something.Just run it outside the chunk and it will work. 

```{r}
rm(list = ls())

require(Zelig)
require(zeligverse)
require(stargazer)
```

Read the data set. Add the correct wd before. 

```{r}

df <- read.csv("in/data-input/FCC_Press_Releases_data.csv")

```

# Descriptives

Show some descriptives and central tendencies

```{r}

psych::describe(df)

```

# Step 1: Run the model, Logit with fixed effects for years

```{r}

# Model 1
z.out_0 <- zelig(pr_dummy ~ oral
               + sep_op
               + status_quo
               + lower_co_uncons
               + bvf 
               + bvl
               + bvr
               + bve
               + bvg
               + factor(year)
               , model = "logit"
               , data = df)

# Model 2, with control variables
z.out <- zelig(pr_dummy ~ oral
               + sep_op
               + status_quo
               + lower_co_uncons
               + bvf 
               + bvl
               + bvr
               + bve
               + bvg
               + second_senate_dummy
               + decision_type
               + count
               + prior_attention
               + factor(year)
               , model = "logit"
               , data = df)

summary(z.out)

```

Create a latex table with the stargazer package

```{r}
stargazer(glm(z.out_0$zelig.out$z.out[[1]], family=binomial(link = "logit")),glm(z.out$zelig.out$z.out[[1]],family=binomial(link = "logit")),
          title="Logistic regressions fixed effects and robust standard errors", type="text"
          ,font.size = "scriptsize"
          , align=TRUE
          , dep.var.labels= "Press release publication", 
          covariate.labels=c("Oral hearing" 
                             , "Dissenting opinion"
                             , "Status quo change" 
                             , "Lower court overruling"
                             , "Abstract review (BvF)" 
                             , "Concrete review (BvL)"
                             , "Constitutional complaint (BvR)"
                             ,"Constitutional dispute between federal organs (BvE)"
                             ,"Dispute between federation and länder (BvG)"
                             , "Second senate"
                             , "Judgment"
                             , "Length of court ruling"
                             ,"Prior media attention"
                            
          ),
          df=FALSE)

```

# Calculate the predicted probabilities by variable

## Model 1

## Oral hearing
```{r}

set.seed(1234)
x.out1 <- setx(z.out_0, oral = 1)
s.out1 <- sim(z.out_0, x = x.out1)
summary(s.out1)

# first difference
set.seed(1234)
x.high <- setx(z.out_0, oral = 1)
x.low <- setx(z.out_0, oral = 0) 
s.out2 <- sim(z.out, x = x.low, x1 = x.high)
summary(s.out2)

# Significant

# for the first diff plot

o <- s.out2$sim.out$x1$fd
o1 <- mean(o[[1]])
o2 <- sd(o[[1]])

# 95% CI 
cilfd_o95 <- o1-(1.96*o2)
ciufd_o95 <- o1+(1.96*o2)

```

## Dissenting opinion
```{r}

set.seed(1234)
x.out1 <- setx(z.out_0, sep_op = 1)
s.out1 <- sim(z.out_0, x = x.out1)
summary(s.out1)

# first difference
set.seed(1234)
x.high <- setx(z.out_0, sep_op = 1)
x.low <- setx(z.out_0, sep_op = 0) 
s.out2 <- sim(z.out, x = x.low, x1 = x.high)
summary(s.out2)

# Significant

# for the first diff plot

s <- s.out2$sim.out$x1$fd
s1 <- mean(s[[1]])
s2 <- sd(s[[1]])

# 95% CI 
cilfd_s95 <- s1-(1.96*s2)
ciufd_s95 <- s1+(1.96*s2)

```

## Status quo change
```{r}

set.seed(1234)
x.out1 <- setx(z.out_0, status_quo = 1)
s.out1 <- sim(z.out_0, x = x.out1)
summary(s.out1)

# first difference
set.seed(1234)
x.high <- setx(z.out_0, status_quo = 1)
x.low <- setx(z.out_0, status_quo = 0) 
s.out2 <- sim(z.out, x = x.low, x1 =x.high)
summary(s.out2)

# Significant

# for the first diff plot

sq <- s.out2$sim.out$x1$fd
sq1 <- mean(sq[[1]])
sq2 <- sd(sq[[1]])

# 95% CI 
cilfd_sq95 <- sq1-(1.96*sq2)
ciufd_sq95 <- sq1+(1.96*sq2)

```


## Lower court overruling
```{r}

set.seed(1234)
x.out1 <- setx(z.out_0, lower_co_uncons = 1)
s.out1 <- sim(z.out_0, x = x.out1)
summary(s.out1)

# first difference
set.seed(1234)
x.high <- setx(z.out_0, lower_co_uncons = 1)
x.low <- setx(z.out_0, lower_co_uncons = 0) 
s.out2 <- sim(z.out_0, x =x.low , x1 =x.high )
summary(s.out2)

# not significant

# for the first diff plot

lcr <- s.out2$sim.out$x1$fd
lcr1 <- mean(lcr[[1]])
lcr2 <- sd(lcr[[1]])

# 95% CI 
cilfd_lcr95 <- lcr1-(1.96*lcr2)
ciufd_lcr95 <- lcr1+(1.96*lcr2)

```

## Abstract review
```{r}

set.seed(1234)
x.out1 <- setx(z.out_0, bvf = 1)
s.out1 <- sim(z.out_0, x = x.out1)
summary(s.out1)

# first difference
set.seed(1234)
x.high <- setx(z.out_0, bvf = 1)
x.low <- setx(z.out_0, bvf = 0) 
s.out2 <- sim(z.out, x = x.low, x1 =x.high )
summary(s.out2)

# not significant

# for the first diff plot

ar <- s.out2$sim.out$x1$fd
ar1 <- mean(ar[[1]])
ar2 <- sd(ar[[1]])

# 95% CI 
cilfd_ar95 <- ar1-(1.96*ar2)
ciufd_ar95 <- ar1+(1.96*ar2)

```

## Concrete review
```{r}

set.seed(1234)
x.out1 <- setx(z.out_0, bvl = 1)
s.out1 <- sim(z.out_0, x = x.out1)
summary(s.out1)

# first difference
set.seed(1234)
x.high <- setx(z.out_0, bvl = 1)
x.low <- setx(z.out_0, bvl = 0) 
s.out2 <- sim(z.out, x = x.low, x1 =x.high )
summary(s.out2)

# Significant

# for the first diff plot

cr <- s.out2$sim.out$x1$fd
cr1 <- mean(cr[[1]])
cr2 <- sd(cr[[1]])

# 95% CI 
cilfd_cr95 <- cr1-(1.96*cr2)
ciufd_cr95 <- cr1+(1.96*cr2)

```

## Constitutional complaint
```{r}

set.seed(1234)
x.out1 <- setx(z.out_0, bvr = 1)
s.out1 <- sim(z.out_0, x = x.out1)
summary(s.out1)

# first difference
set.seed(1234)
x.high <- setx(z.out_0, bvr = 1)
x.low <- setx(z.out_0, bvr = 0) 
s.out2 <- sim(z.out, x = x.low, x1 =x.high)
summary(s.out2)

# Significant

# for the first diff plot

cc <- s.out2$sim.out$x1$fd
cc1 <- mean(cc[[1]])
cc2 <- sd(cc[[1]])

# 95% CI 
cilfd_cc95 <- cc1-(1.96*cc2)
ciufd_cc95 <- cc1+(1.96*cc2)

```

## Constitutional dispute between federal organs
```{r}

set.seed(1234)
x.out1 <- setx(z.out_0, bve = 1)
s.out1 <- sim(z.out_0, x = x.out1)
summary(s.out1)

# first difference
set.seed(1234)
x.high <- setx(z.out_0, bve = 1)
x.low <- setx(z.out_0, bve = 0) 
s.out2 <- sim(z.out, x = x.low, x1 =x.high )
summary(s.out2)

# Significant

# for the first diff plot

df <- s.out2$sim.out$x1$fd
df1 <- mean(df[[1]])
df2 <- sd(df[[1]])

# 95% CI 
cilfd_df95 <- df1-(1.96*df2)
ciufd_df95 <- df1+(1.96*df2)

```

## Dispute between federation and länder

```{r}

set.seed(1234)
x.out1 <- setx(z.out_0, bvg = 1)
s.out1 <- sim(z.out_0, x = x.out1)
summary(s.out1)

# first difference
set.seed(1234)
x.high <- setx(z.out_0, bvg = 1)
x.low <- setx(z.out_0, bvg = 0) 
s.out2 <- sim(z.out, x = x.low, x1 =x.high )
summary(s.out2)

# Significant

# for the first diff plot

dfl <- s.out2$sim.out$x1$fd
dfl1 <- mean(dfl[[1]])
dfl2 <- sd(dfl[[1]])

# 95% CI 
cilfd_dfl95 <- dfl1-(1.96*dfl2)
ciufd_dfl95 <- dfl1+(1.96*dfl2)

```

## Plot first differences for the first model 
```{r}
plot(seq(0:3)
     , las = 1.1
     , type="n"
     , ylim=c(0,4)
     , xlim=c(-1,1)
     , yaxt="n" 
     , ylab = ""
     , xlab="First difference in press release publication (Model 1, incl. 95% CI)"
     , main= "" #"Mean Propability of spatial towards court in different models (incl. 90 % CI)"
     , cex.lab = 1.
     , cex.main = 1
     , frame.plot=F)

legend( x = 0, y = 4.2
        , legend = c("95% Confidence interval")
        , cex = .8
        , bty = "n")

segments(0, 0, 0, 4.4, col="darkgray", lty=2, lwd=1)

# Oral
points(o1, .1, pch=20, cex=1.5, col="black")           
segments(cilfd_o95, .1, ciufd_o95, .1, col="black", lty=1, lwd=1.5, lend=0)
text(-.8, .4, "Oral hearing", pos = 1,  srt=0, xpd = TRUE, cex = .8,  col = "black")

# Dissent
points(s1, .5, pch=20, cex=1.5, col="black")           
segments(cilfd_s95, .5, ciufd_s95, .5, col="black", lty=1, lwd=1.5, lend=0)
text(-.8, .8, "Dissenting opinion", pos = 1,  srt=0, xpd = TRUE, cex = .8,  col = "black")

# Status quo
points(sq1, .95, pch=20, cex=1.5, col="black")           
segments(cilfd_sq95, .95, ciufd_sq95, .95, col="black", lty=1, lwd=1.5, lend=0)
text(-.8, 1.25, "Status quo change", pos = 1,  srt=0, xpd = TRUE, cex = .8,  col = "black")

# Abstract review
points(ar1, 1.3, pch=20, cex=1.5, col="black")           
segments(cilfd_ar95, 1.3, ciufd_ar95, 1.3, col="black", lty=1, lwd=1.5, lend=0)
text(-.8, 1.65, "Abstract review", pos = 1,  srt=0, xpd = TRUE, cex = .8,  col = "black")

# Concrete review
points(cr1, 1.7, pch=20, cex=1.5, col="black")           
segments(cilfd_cr95, 1.7, ciufd_cr95, 1.7, col="black", lty=1, lwd=1.5, lend=0)
text(-.8, 2.05, "Concrete review", pos = 1,  srt=0, xpd = TRUE, cex = .8,  col = "black")

# Constitutional complaint
points(cc1, 2.15, pch=20, cex=1.5, col="black")           
segments(cilfd_cc95, 2.15, ciufd_cc95, 2.15, col="black", lty=1, lwd=1.5, lend=0)
text(-.8, 2.45, "Constitutional complaint", pos = 1,  srt=0, xpd = TRUE, cex = .8,  col = "black")

# Dispute federal organs
points(df1, 2.55, pch=20, cex=1.5, col="black")           
segments(cilfd_df95, 2.55, ciufd_df95, 2.55, col="black", lty=1, lwd=1.5, lend=0)
text(-.8, 2.9, "Federal dispute", pos = 1,  srt=0, xpd = TRUE, cex = .8,  col = "black")

# Dispute länder
points(dfl1, 3.05, pch=20, cex=1.5, col="black")           
segments(cilfd_dfl95, 3.05, ciufd_dfl95, 3.05, col="black", lty=1, lwd=1.5, lend=0)
text(-.8, 3.35, "Länder dispute", pos = 1,  srt=0, xpd = TRUE, cex = .8,  col = "black")

# lower court  over ruling 
points(lcr1, 3.5, pch=20, cex=1.5, col="black")           
segments(cilfd_lcr95, 3.5, ciufd_lcr95, 3.5, col="black", lty=1, lwd=1.5, lend=0)
text(-.8, 3.8, "Lower court overruling", pos = 1,  srt=0, xpd = TRUE, cex = .8,  col = "black")


```

# Predicted probabilities for Model 2

## Oral hearing

```{r}
set.seed(1234)
x.out1 <- setx(z.out, oral = 1)
s.out1 <- sim(z.out, x = x.out1)
summary(s.out1)


# first difference
set.seed(1234)
x.high <- setx(z.out, oral = 1)
x.low <- setx(z.out, oral = 0) 
s.out2 <- sim(z.out, x =x.low , x1 =x.high )
summary(s.out2)

# not significant
```

## Separate opinion

```{r}

set.seed(1234)
x.out1 <- setx(z.out, sep_op = 1)
s.out1 <- sim(z.out, x = x.out1)
summary(s.out1)

# first difference
set.seed(1234)
x.high <- setx(z.out, sep_op = 1)
x.low <- setx(z.out, sep_op = 0) 
s.out2 <- sim(z.out, x =x.low , x1 =x.high )
summary(s.out2)

# not significant

```

## Status quo change

```{r}
set.seed(1234)
x.out1 <- setx(z.out, status_quo = 1)
s.out1 <- sim(z.out, x = x.out1)
summary(s.out1)

# first difference
set.seed(1234)
x.high <- setx(z.out, status_quo = 1)
x.low <- setx(z.out, status_quo = 0) 
s.out2 <- sim(z.out, x = x.low, x1 =x.high )
summary(s.out2)


# Significant

# for the first diff plot

sq2.1 <- s.out2$sim.out$x1$fd
sq2.2 <- mean(sq2.1[[1]])
sq2.3 <- sd(sq2.1[[1]])

# 95% CI 
cilfd_sq2.95 <- sq2.2-(1.96*sq2.3)
ciufd_sq2.95 <- sq2.2+(1.96*sq2.3)

```

## Lower court overruling

```{r}
set.seed(1234)
x.out1 <- setx(z.out, lower_co_uncons = 1)
s.out1 <- sim(z.out, x = x.out1)
summary(s.out1)

# first difference
set.seed(1234)
x.high <- setx(z.out, lower_co_uncons = 1)
x.low <- setx(z.out, lower_co_uncons = 0) 
s.out2 <- sim(z.out, x = x.low, x1 = x.high )
summary(s.out2)

# not significant

```

## Abstract reviews

```{r}

set.seed(1234)
x.out1 <- setx(z.out, bvf = 1)
s.out1 <- sim(z.out, x = x.out1)
summary(s.out1)

# first difference
set.seed(1234)
x.high <- setx(z.out, bvf = 1)
x.low <- setx(z.out, bvf = 0) 
s.out2 <- sim(z.out, x = x.low, x1 =x.high )
summary(s.out2)

# not significant

```

## Concrete reviews

```{r}
set.seed(1234)
x.out1 <- setx(z.out, bvl = 1)
s.out1 <- sim(z.out, x = x.out1)
summary(s.out1)


# first difference
set.seed(1234)
x.high <- setx(z.out, bvl = 1)
x.low <- setx(z.out, bvl = 0) 
s.out2 <- sim(z.out, x =x.low , x1 =x.high )
summary(s.out2)

# Significant

# for the first diff plot

cr2.1 <- s.out2$sim.out$x1$fd
cr2.2 <- mean(cr2.1[[1]])
cr2.3 <- sd(cr2.1[[1]])

# 95% CI 
cilfd_cr2.95 <- cr2.2-(1.96*cr2.3)
ciufd_cr2.95 <- cr2.2+(1.96*cr2.3)

```


## Constitutional complaint

```{r}
set.seed(1234)
x.out1 <- setx(z.out, bvr = 1)
s.out1 <- sim(z.out, x = x.out1)
summary(s.out1)

# first difference
set.seed(1234)
x.high <- setx(z.out, bvr = 1)
x.low <- setx(z.out, bvr = 0) 
s.out2 <- sim(z.out, x = x.low, x1 =x.high )
summary(s.out2)

# not significant

```

## Constitutional dispute between federal organs

```{r}

set.seed(1234)
x.out1 <- setx(z.out, bve = 1)
s.out1 <- sim(z.out, x = x.out1)
summary(s.out1)


# first difference
set.seed(1234)
x.high <- setx(z.out, bve = 1)
x.low <- setx(z.out, bve = 0) 
s.out2 <- sim(z.out, x = x.low , x1 =x.high )
summary(s.out2)

# Significant

# for the first diff plot

d2.1 <- s.out2$sim.out$x1$fd
d2.2 <- mean(d2.1[[1]])
d2.3 <- sd(d2.1[[1]])

# 95% CI 
cilfd_d2.95 <- d2.2-(1.96*d2.3)
ciufd_d2.95 <- d2.2+(1.96*d2.3)

```

## Dispute between federation and länder

```{r}
set.seed(1234)
x.out1 <- setx(z.out, bvg = 1)
s.out1 <- sim(z.out, x = x.out1)
summary(s.out1)

# first difference
set.seed(1234)
x.high <- setx(z.out, bvg = 1)
x.low <- setx(z.out, bvg = 0) 
s.out2 <- sim(z.out, x = x.low, x1 =x.high )
summary(s.out2)

# Significant

# for the first diff plot

dl2.1 <- s.out2$sim.out$x1$fd
dl2.2 <- mean(dl2.1[[1]])
dl2.3 <- sd(dl2.1[[1]])

# 95% CI 
cilfd_dl2.95 <- dl2.2-(1.96*dl2.3)
ciufd_dl2.95 <- dl2.2+(1.96*dl2.3)

```

## Second senate

```{r}
set.seed(1234)
x.out1 <- setx(z.out, second_senate_dummy = 1)
s.out1 <- sim(z.out, x = x.out1)
summary(s.out1)

# first difference
set.seed(1234)
x.high <- setx(z.out, second_senate_dummy = 1)
x.low <- setx(z.out, second_senate_dummy = 0) 
s.out2 <- sim(z.out, x = x.low , x1 = x.high )
summary(s.out2)

# # Significant

# for the first diff plot

ss2.1 <- s.out2$sim.out$x1$fd
ss2.2 <- mean(ss2.1[[1]])
ss2.3 <- sd(ss2.1[[1]])

# 95% CI 
cilfd_ss2.95 <- ss2.2-(1.96*ss2.3)
ciufd_ss2.95 <- ss2.2+(1.96*ss2.3)

```

## Judgment

```{r}
set.seed(1234)
x.out1 <- setx(z.out, decision_type = 1)
s.out1 <- sim(z.out, x = x.out1)
summary(s.out1)


# first difference
set.seed(1234)
x.high <- setx(z.out, decision_type = 1)
x.low <- setx(z.out, decision_type = 0) 
s.out2 <- sim(z.out, x =x.low , x1 = x.high)
summary(s.out2)

# not significant

```

## Length of court ruling

```{r}
set.seed(1234)
x.out1 <- setx(z.out, count = 122, count = 115240)
s.out1 <- sim(z.out, x = x.out1)
summary(s.out1)

# first difference
set.seed(1234)
x.high <- setx(z.out, count = 115240)
x.low <- setx(z.out, count = 122) 
s.out2 <- sim(z.out, x = x.low, x1 = x.high)
summary(s.out2)

# Significant

# for the first diff plot

le2.1 <- s.out2$sim.out$x1$fd
le2.2 <- mean(le2.1[[1]])
le2.3 <- sd(le2.1[[1]])

# 95% CI 
cilfd_le2.95 <- le2.2-(1.96*le2.3)
ciufd_le2.95 <- le2.2+(1.96*le2.3)

```

## Prior media attention

```{r}
set.seed(1234)
x.out1 <- setx(z.out, prior_attention = 1)
s.out1 <- sim(z.out, x = x.out1)
summary(s.out1)


# first difference
set.seed(1234)
x.high <- setx(z.out,  prior_attention = 1)
x.low <- setx(z.out,  prior_attention = 0)
s.out2 <- sim(z.out, x = x.high, x1 = x.low)
summary(s.out2)

# not significant

```

## Plot first differences for the second model 
```{r}

plot(seq(0:3)
     , las = 1.1
     , type="n"
     , ylim=c(0,4)
     , xlim=c(-1,1)
     , yaxt="n" 
     , ylab = ""
     , xlab="First difference in press release publication (Model 2, incl. 95% CI)"
     , main= "" #"Mean Propability of spatial towards court in different models (incl. 90 % CI)"
     , cex.lab = 1.
     , cex.main = 1
     , frame.plot=F)

legend( x = 0, y = 4.2
        , legend = c("95% Confidence interval")
        , cex = .8
        , bty = "n"
)

segments(0, 0, 0, 4.4, col="darkgray", lty=2, lwd=1)

# Status quo
points(sq2.2, .95, pch=20, cex=1.5, col="black")           
segments(cilfd_sq2.95, .95, ciufd_sq2.95, .95, col="black", lty=1, lwd=1.5, lend=0)
text(-.8, 1.25, "Status quo change", pos = 1,  srt=0, xpd = TRUE, cex = .8,  col = "black")

# Concrete review
points(cr2.2, 1.7, pch=20, cex=1.5, col="black")           
segments(cilfd_cr2.95, 1.7, ciufd_cr2.95, 1.7, col="black", lty=1, lwd=1.5, lend=0)
text(-.8, 2.05, "Concrete review", pos = 1,  srt=0, xpd = TRUE, cex = .8,  col = "black")

# Dispute federal organs
points(d2.2, 2.55, pch=20, cex=1.5, col="black")           
segments(cilfd_d2.95, 2.55, ciufd_d2.95, 2.55, col="black", lty=1, lwd=1.5, lend=0)
text(-.8, 2.9, "Federal dispute", pos = 1,  srt=0, xpd = TRUE, cex = .8,  col = "black")

# Dispute länder
points(dl2.2, 3.5, pch=20, cex=1.5, col="black")         
segments(cilfd_dl2.95, 3.5, ciufd_dl2.95,  3.5, col="black", lty=1, lwd=1.5, lend=0)
text(-.8, 3.8, "Länder dispute",  pos = 1,  srt=0, xpd = TRUE, cex = .8,  col = "black")

# --- Control variables

# Second Senate
points(ss2.2, .1, pch=20, cex=1.5, col="black")           
segments(cilfd_ss2.95, .1, ciufd_ss2.95, .1, col="black", lty=1, lwd=1.5, lend=0)
text(-.8, .4, "Second senate", pos = 1,  srt=0, xpd = TRUE, cex = .8,  col = "black")

# Length
points(le2.2, .5, pch=20, cex=1.5, col="black")           
segments(cilfd_le2.95, .5, ciufd_le2.95, .5, col="black", lty=1, lwd=1.5, lend=0)
text(-.8, .8, "Length of court ruling", pos = 1,  srt=0, xpd = TRUE, cex = .8,  col = "black")

```

# Additional analysis to control for institutional-based interaction terms

In the following Logit regressions with interaction effects will be shown. This controls for potential effects due to the institutional organization of the FCC, which is splitted into two senates with slightly different competencies.

```{r}

# Load the data again

df <- read.csv("/in/data-input/FCC_Press_Releases_data.csv")

```


## Run the model with interaction terms
```{r}

z.out_i <- zelig(pr_dummy ~ oral
                 + sep_op
                 + status_quo
                 + lower_co_uncons
                 + bvf*second_senate_dummy 
                 + bvl*second_senate_dummy 
                 + bvr*second_senate_dummy 
                 + bve
                 + bvg
                 + second_senate_dummy
                 + decision_type
                 + count
                 + prior_attention
                 + factor(year)
                 , model = "logit"
                 , data = df)

summary(z.out_i)

```

## Latex table
```{r}

stargazer(glm(z.out_0$zelig.out$z.out[[1]], family=binomial(link = "logit")),glm(z.out$zelig.out$z.out[[1]],family=binomial(link = "logit")),glm(z.out_i$zelig.out$z.out[[1]],family=binomial(link = "logit")),
          title="Logistic regressions fixed effects and robust standard errors", type="text"
          ,font.size = "scriptsize"
          , align=TRUE
          , dep.var.labels= "Press release publication", 
          covariate.labels=c("Oral hearing" 
                             , "Dissenting opinion"
                             , "Status quo change" 
                             , "Lower court overruling"
                             , "Abstract review (BvF)" 
                             , "Concrete review (BvL)"
                             , "Constitutional complaint (BvR)"
                             ,"Constitutional dispute between federal organs (BvE)"
                             ,"Dispute between federation and länder (BvG)"
                             , "Second senate"
                             , "Judgment"
                             , "Length of court ruling"
                             , "Prior media attention"
                             #, "Abstract review (BvF)*Second senate" 
                             #, "Concrete review (BvL)*Second senate"
                             #, "Constitutional complaint (BvR)*Second senate"
                             
          ),
          df=FALSE)


```

